
\section{Implementation}
\label{sec:implementation}

\subsection{Components Overview}

We implemented \sys on Linux 6.15, extending the kernel with a standalone file ($\sim$1 KLOC) that handles hook registration and verifier extensions. We integrated lightweight instrumentation ($\sim$100 LOC) into NVIDIA's open GPU kernel modules to expose memory management and scheduling decision points (\S\ref{sec:impl-host}). Our userspace loader and JIT infrastructure ($\sim$10 KLOC) builds upon bpftime's framework, while an LLVM-based backend ($\sim$1 KLOC) translates the restricted \sys eBPF instruction subset into GPU device code (PTX) (\S\ref{sec:impl-gpu}).

\subsection{Host-side Integration}
\label{sec:impl-host}

\sys extends the NVIDIA Open GPU Kernel Modules~\cite{nvidia-open-gpu}, instrumenting the UVM module at page fault handler and prefetch logic. At each hook, the driver constructs a context containing fields (e.g., region range aligned to 2MB GPU physical chunks, VA blocks or 4KB pages, fault address, block size) and invokes an attached eBPF handler. Currently, eviction hooks operate at 2MB block granularity, while prefetch hooks operate at page granularity. Each handler returns a decision to execute or bypass default kernel logic. The kernel maintains a doubly-linked eviction list; handlers may reorder regions via provided helpers, but the kernel retains eviction authority under memory pressure.

We instrument Time-Slice Group (TSG) lifecycle events, including initialization (\texttt{task\_init}) and teardown (\texttt{task\_destroy}). The eBPF policy can configure scheduling parameters such as TSG priority, timeslice duration, and runlist interleave frequency via the \texttt{bpf\_gpu\_set\_attr} kfunc, and can reject task binding via the \texttt{bpf\_gpu\_reject\_bind} kfunc. Our kernel module extends the Linux eBPF verifier by registering GPU-specific struct\_ops and kfunc interfaces, leveraging BTF annotations to enforce type and memory safety.

\subsection{GPU Runtime}
\label{sec:impl-gpu}

After the Linux kernel verifies a \sys device eBPF program, our loader forwards bytecode and BTF metadata to a userspace backend, translating the restricted eBPF subset into GPU PTX code. We reuse Linux's eBPF verifier to enforce standard memory safety, bounded loops, and type correctness. An additional verifier pass leverages BTF metadata annotations that mark warp-uniform fields: at load time, our verifier performs dataflow analysis on eBPF bytecode, propagating warp-uniformity through arithmetic, logical, and memory operations. Control-flow constraints are enforced by traversing the policy's CFG to reject lane-varying dependencies in branch predicates or loop bounds. Map-update instructions must use warp-uniform keys derived from uniform registers or warp-level reductions. GPU-wide barriers, global synchronization primitives, and non-uniform atomics are disallowed by pattern-matching. Each hook type carries resource budgets limiting instructions, helper invocations, and memory operations. 

Before each GPU kernel runs, \sys dynamically intercepts CUDA runtime APIs to extract GPU kernel PTX, rewrite it with binary trampolines, and load instrumented GPU kernels back without recompilation or restarting the application. These trampolines, placed at GPU kernel entry, selected memory instructions (such as global loads and atomic operations), and execution-phase boundaries, insert prologue/epilogue logic for SIMT register preservation. In each trampoline, per-lane inputs are aggregated using \texttt{\_\_ballot\_sync} and \texttt{\_\_shfl\_sync}, with a warp leader selected via \texttt{\_\_ffs(\_\_activemask())} to execute the scalar eBPF handler once per warp, broadcasting results via shuffle instructions; verified eBPF code executes after kernel launch, supported by pre-compiled GPU helper functions. During JIT compilation, we inline helper functions and map accesses to reduce call overhead. For scheduling, \sys implements policies using persistent GPU workers as long-lived kernels that poll and claim logical work units; on Blackwell GPUs, we use cluster launch control APIs to schedule thread blocks. For memory management instrumentation, \sys attaches eBPF policy at memory instructions, GPU kernel function boundaries, and tracepoints to issue policy hints to the host driver. Unlike our prior work eGPU~\cite{egpu} which relies on atomic synchronization, \sys{} avoids cross-SM synchronization primitives to prevent hardware stalls.

\paragraph{Hierarchical Maps and Cross-Domain State}

We use eBPF maps in GPU-accessible memory as a shared state abstraction between host-driver and GPU-device contexts. Map shards are placed according to access patterns: cold global state resides in host DRAM and is periodically refreshed from GPU-side snapshots; frequently accessed state resides in GPU global memory and is asynchronously flushed to host; hot per-warp or per-SM data is cached in GPU shared memory for low latency. Consistency across shards is maintained via snapshot-based aggregation at GPU kernel completion boundaries. A runtime daemon asynchronously flushes GPU-local shards to host-visible canonical map instances, providing coherent snapshots to host-side policies without synchronization overhead. Shard updates occur strictly at warp granularity through warp-leader threads without GPU atomic operations. For example, GPU-side handlers accumulate per-region access counters in warp-local registers, aggregate them per warp, and store results into GPU-local shards. The periodic snapshot flush transfers these shards to the host for policy decisions.