\begin{abstract}
Performance in modern GPU-centric systems increasingly depends on resource management policies, including memory placement, scheduling, and observability. However, uniform policies typically yield suboptimal performance across diverse workloads. Existing approaches present a tradeoff: user-space runtimes provide programmability and flexibility but lack cross-tenant visibility and fine-grained control of hardware resources; meanwhile, modifications to the OS kernel introduce significant complexity and safety risks. To address this, we argue that the GPU driver and device layer should provide an extensible OS interface for policy enforcement. While the emerging eBPF technology shows potential, directly applying existing host-side eBPF is insufficient because they lack visibility and control into critical device-side events, and directly embedding policy code into GPU kernels could compromise safety and efficiency.

We propose \sys, an eBPF-based runtime that treats the GPU driver and device as a programmable OS subsystem. \sys extends GPU drivers by exposing safe programmable hooks and introduces a device-side eBPF runtime capable of executing verified policy logic within GPU kernels, enabling coherent and transparent policies. Evaluation across realistic workloads including inference, training, and vector search demonstrates that \sys improves throughput by up to $4.8\times$ and reduces tail latency by up to $2\times$, incurring minimal overhead, without modifying or restarting applications.
% \xiangyu{I think it is better to reduce the abstract content by 50-60\% by removing some example details.}
% \yusheng{should we use general "policy" or make it resources management policy? we are also doing  optimization for a single application and doing observability/tracing}
% \JC{
% Resource management policies have become crucial in modern GPU systems, as diverse workloads contend for limited resources in multi-tenant environments. However, current approaches to policy specification and enforcement are inadequate. Policies are either hard-coded into opaque drivers or scattered across user-space runtimes, lacking flexibility, coordination, and strong safety guarantees.

% We propose exposing the GPU driver and device layer as a programmable resource management substrate using eBPF, enabling application-transparent policies with stack-wide coordination, full hardware control, and strong safety guarantees. \sys introduces a verifiable runtime that executes management policies within the GPU stack, ensuring policy code is checked for bounded execution and memory access. This allows policies to dynamically adapt to workload requirements while guaranteeing system stability. Our evaluation on real-world workloads shows that \sys improves


% }
\end{abstract}

\section{Introduction}

% 1. (General problem) GPU is important (1). Motivate the resources management policy is important (resource mpolicy has emerged as ... 
% 2. (The problem with current works) Current design rigiet for us to create new resource management policy, some one has try to modify drivers; others are trying to do it in usersapce framwork
% 3. Our key insight is that the GPU driver is uniquely positiooned in the GPU stack to have transparency into all applications, etc. 
% 4. (Our claim) In this paper, we present \sys{}, a new system that enables flexible resource management policies for GPU deployments.  Building on our key insight, \sys{} implements a stable set of control plane hooks that allow for flexible resource managment policies...
% 5. To support flexibile policies, applications must be able to observe an application's behavior on the GPU device. Safety is required... Thus, we implement our SIMT verifier. 
%6. Finally, to allow the driver and device components to communicate, we need a communication substrate.
%7. We implemented \sys{} on.... We evaluated on xyz workloads and our results are awesome. 
%8. Our contributions are as follows: 
%   a. 


% 1. (General problem) GPU is important (1). Motivate the resources management policy is important (resource mpolicy has emerged as ...
The performance and efficiency of GPU-based systems increasingly depend not only on raw compute and memory performance but also on resource management policies. GPUs account for a growing share of compute resources in modern systems~\cite{jeon2019analysis}, supporting diverse workloads such as latency-sensitive inference~\cite{kwon2023efficient,agrawal2024taming,yu2024orca}, compute-intensive training~\cite{shoeybi2019megatron,rasley2020deepspeed}, graph analytics~\cite{lin2024towards,chen2020pangolin,wang2016gunrock}, vector search~\cite{pan2024survey,cao2023gpu}, and data visualization~\cite{moreland2016vtk}, each imposing distinct and often conflicting resource requirements. GPU software stacks, spanning user-space frameworks, OS kernel drivers, vendor firmware, and device-side kernel code, necessitate coordination of memory placement and migration~\cite{sun2024llumnix,zhong2024distserve,patel2024splitwise,strati2024orion,sheng2023flexgen}, kernel scheduling in multi-tenant environments~\cite{fu2024serverlessllm,shubha2024usher,hu2023lucid,li2022miso,jayaram2023sia,xiao2018gandiva,narayanan2020heterogeneity}, and dynamic observability for online adaptation~\cite{agrawal2024vidur}. These policies must evolve alongside changing hardware architectures, emerging workloads, and varying service-level agreements (SLAs)~\cite{kwon2023efficient,yu2020fine,delimitrou2013paragon,delimitrou2014quasar,lo2015heracles,qiao2021pollux}.

Given these diverse and evolving requirements, no single policy fits all scenarios. Recent work confirms that default Unified Virtual Memory (UVM) placement policies~\cite{wang2024suv,lin2025forest,kim2025dream,liao2024svm,park2025helm} and scheduling policies~\cite{wang2024gcaps,fan2025gpreempt,kato2011timegraph,shen2025xsched} can perform poorly across workloads and lack multi-tenant coordination on different deployments.

% 2. (The problem with current works) Current design rigiet for us to create new resource management policy, some one has try to modify drivers; others are trying to do it in usersapce framwork
Unfortunately, existing programmable GPU resource management policy solutions force developers into tradeoffs between user-space methods that lack global visibility and control over system-level GPU behaviors, and kernel-level implementations that introduce complexity and safety risks. 
Concretely, user-space frameworks~\cite{ng2023paella,shen2025xsched,gim2025pie,chen2025ktransformers} offer programmability, but lack cross-application visibility and management of low-level GPU mechanisms (e.g. thread timeslices and replayable page faults~\cite{fan2025gpreempt,nvidia-open-gpu}). These approaches bind to specific runtime frameworks, requiring application-level code changes and limiting portability and reuse. Conversely, kernel-based resource management approaches~\cite{kato2011timegraph,kato2012gdev,kernelintercept,fan2025gpreempt,wang2024gcaps} provide visibility and control of GPU hardware states, their direct modification on static, vendor-specific kernel modules making them difficult to deploy and maintain, and posing stability concerns. GPU profiling frameworks~\cite{cupti,villa2019nvbit,neutrino}, including our prior workshop version~\cite{egpu}, enable kernel-level observation but lack runtime programmability and driver integration, limiting adaptive resource management.

% 3. Our key insight is that the GPU driver is uniquely positiooned in the GPU stack to have transparency into all applications, etc.
To address this, we argue that GPU resource management requires \textbf{an 
OS policy interface for GPU} providing safe, flexible and transparent programmability. The GPU driver layer is positioned to offer global visibility, enable cross-tenant coordination, and provide fine-grained management of privileged low-level GPU mechanisms without requiring application modifications. Recent CPU-side frameworks, such as eBPF, have demonstrated the feasibility of dynamic, kernel-level policy programmability with safety guarantees~\cite{bachl2021flow,Zhong22,jia2023programmable,schedext-docs,zussman2025cache_ext}. Inspired by its success, we propose treating GPU resource management as a first-class programmable OS subsystem. However, naively extending host-only eBPF remains insufficient because scheduling and memory management decisions such as thread-block dispatch, warp-level execution scheduling, and memory synchronization occur within GPU hardware and remain invisible and uncontrollable from the host. Thus, a practical solution must expose programmable policy hooks within GPU drivers and execute verified policy logic inside GPU kernels.

We present \sys{}, a cross-layer policy runtime that transforms the GPU driver and device into a programmable OS subsystem. \sys{} exposes stable, verified control-plane hooks within the GPU driver, enabling safe and customized programmable resource management policies. 
\sys{} further supports injecting verified eBPF policy logic into GPU kernels, providing consistent and transparent policy enforcement across the host-device boundary.

Designing \sys{} has three technical challenges to solve: \textbf{C1:} Exposing low-level driver mechanisms provides expressiveness but risks instability; we balance this tension with a narrow policy interface built around hardware-aligned abstractions (\S\ref{sec:design-interfaces}). \textbf{C2:} Scalar eBPF semantics conflict with GPU SIMT parallelism, causing divergence and deadlocks. Thus, we introduce a SIMT-aware verifier and warp-level execution model for optimization (\S\ref{sec:verification}). \textbf{C3:} Host-device memory hierarchies differ in latency and consistency; we bridge them with cross-layer eBPF maps using relaxed consistency (\S\ref{sec:verification}).


We implement \sys{} on Linux by extending the NVIDIA open GPU kernel modules~\cite{nvidia-open-gpu} and providing an eBPF runtime for GPU devices. We evaluate \sys across GPU workloads including LLM inference pipelines, GNN training, vector search, and mixed-priority multi-tenant scenarios. Using \sys, we implement adaptive memory prefetching and eviction policies, fine-grained kernel preemption strategies, dynamic work-stealing schedulers, and programmable GPU kernel observability tools. \sys-based policies improve throughput by up to $4.8\times$ and reduce tail latency by up to $2\times$ compared to static heuristics, while instrumentation-only deployments incur low overhead. This demonstrates that cross-layer eBPF-based programmability spanning host and device is an effective abstraction for GPU-centric systems. In summary, our contributions are:

\begin{itemize}[leftmargin=*,itemsep=0pt]
  \item We design an extensible OS policy interface for GPU memory, scheduling, and observability.

  \item We implement \sys, an eBPF runtime with SIMT-aware verification spanning host driver and GPU device.

  \item We show \sys policies improve throughput and reduce tail latency across inference, training, and search workloads.
\end{itemize}
